### 2020-01-16 methods.tex
updated methods, etc

\paragraph{Normalization of Empirical Matrices}.  Formally, to apply RMT, we would usually define Correlation Matrix with $\dfrac{1}{N}$ normalization,
and assume that either the variance of $\mathbf{X}$ is unity, $\sigma^{2}=1$, or is known.
\footnote{And for formal proofs of the Heavy Tailed results, we need a different normalization,$\dfrac{1}{N^{1-\alpha}}$}
But for these empirical studies, the pretrained DNNs are typically initialized with random weight matrices $\mathbf{W}_{0}$ ,
with the variance already normalized to $\sqrt{\frac{1}{N}}$, or some variant of this such as Glorot (or Xavier) Normalization\cite{GloRot},
or as $\sqrt{\frac{2}{N*k^2}}$ for Convolutional 2D Layers. 
We do not normalize (or renormalize) the Empirical Correlation Matrices, and use them as-is,
except that we rescale the Conv2D pre-Activation Maps $\mathbf{W}_{i,L}$ by $\frac{k}{\sqrt{2}}$ so that they
are on the same scale as the Linear layers.
Note that in some pretrinaed models, like the pyTorch VGG models, the Linear weight matrices appear to have been 
initialized with variance $\sigma\sim0.01$.  We do not attempt to correct for this, and, instead, simply try to treat all
models the same.  
Also, The normalization does not affect the Power Law fits because the Heavy Tailed exponent $\alpha$ is scale-invariant.
As are metrics like the Stable Rank and our MP Soft Rank. In this study, however, all of the metrics strongly depend 
on the scale of the weight matrix.

>>>>

\paragraph{Normalization of Empirical Matrices}.  
The normalization does not affect the Power Law fits because the Heavy Tailed exponent $\alpha$ is scale-invariant.
As are metrics like the Stable Rank and our MP Soft Rank. In this study, however, all of the metrics strongly depend 
on the scale of the weight matrix.
Formally, to apply RMT, we would usually define Correlation Matrix with $\dfrac{1}{N}$ normalization,
and assume that either the variance of $\mathbf{X}$ is unity, $\sigma^{2}=1$, or is known.
\footnote{And for formal proofs of the Heavy Tailed results, we need a different normalization,$\dfrac{1}{N^{1-\alpha}}$}
But for these empirical studies, the pretrained DNNs are typically initialized with random weight matrices $\mathbf{W}_{0}$ ,
with the variance already normalized to $\sqrt{\frac{1}{N}}$, or some variant of this such as Glorot (or Xavier) Normalization\cite{GloRot},
or as $\sqrt{\frac{2}{N*k^2}}$ for Convolutional 2D Layers. 
We do not normalize (or renormalize) the Empirical Correlation Matrices, and use them as-is,
except that we rescale the Conv2D pre-Activation Maps $\mathbf{W}_{i,L}$ by $\frac{k}{\sqrt{2}}$ so that they
are on the same scale as the Linear layers.

Note that in some pretrained models, like the pyTorch VGG models, the Linear weight matrices appear to have been 
initialized with variance $\sigma\sim0.01$.  We do not attempt to correct for this, and, instead, simply try to treat all
models the same.

However, in the GPT2 and other NLP models, we find that the first embedding layer(s) have unusually large eigenvalues,
reflecting a lack of normalization.  For example, in GPT, most layers, the maximum eigenvalue $\lambda_{max}\sim\mathcal{O}(10-100)$, 
but in the first embedding layer, the maximum is of order N (the number of words in the embedding), or
 $\lambda_{max}\sim\mathcal{O}(10^{5})$.  For GPT and GPT2, we layer all layers as-is (although one may to normalize
the first 2 layers by  $\mathbf{X}$ by $\frac{1}{N}$, or to treat them as an outlier); including them does
not significantly alter the results here.

COMMENT ON HOW LOG NORM first and last layers behave, maybe somewhere else

COMMENT ON HOW LOG PORM  for GPT includes unusually high alpha, not meaningful other than to show the trend.

### 2020-01-16 nlp_models.tex
updated discussion on first layer in GPT2
updated methods, etc

@@

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|}
\hline
   &    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
 Series & \#Layers   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{\infty}$ & $\hat{\alpha}=\alpha\log\lambda_{max}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
\hline
 GPT & & & & &\\
 GPT2 (small) & & & & & \\
 GPT2-medium & & & & & \\
 GPT2-large & & & & & \\
 GPT2-xl & & & & &\\

>>>>

[THESE RESULTS HAVE TO BE REDONE BY REMOVING THE FIRST LAYER...]

@@

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|}
\hline
   &    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
 Series & \#Layers   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{\infty}$ & $\hat{\alpha}=\alpha\log\lambda_{max}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
\hline
 GPT & & & & &\\
GPT2 & 50 & 2.05 &2.59& 9.78 & 10.03 \\
GPT2 medium & 98 & 2.08 &2.58& 9.74 & 10.01 \\
GPT2 large & 146 & 1.85 &1.99& 7.67 & 7.94 \\
GPT2 xl & 194 & 1.86 &1.92& 7.17 & 7.51 \\

Explain why Log Norm is sooo large...alpha is off may need to prune the alpha
